### 2023-10-17 latex/paper/main.tex
abstract refining

\section{Abstract}
Our study explores the performance of distributed linear algebra operations executed in both serial and parallel modes across varying matrix sizes. We find that serial execution outperforms parallel execution, especially for smaller matrices, but as matrix size increases, the performance gap widens. This suggests that parallelization's overhead can outweigh its advantages for larger matrices. Additionally, standard deviation in execution times increases with matrix size. Our case study uses the Ray framework on a 10-computer cluster provided by the University of Messina. The cluster's 8GB of RAM supports our comprehensive tests of determinant, dot product, matrix inversion, and rank calculations across different matrix sizes. This research contributes insights for optimizing distributed computing in the era of big data and scalable computation.

>>>>

\section{Abstract}
Our study explores the performance of distributed linear algebra operations executed in both serial and parallel modes across varying matrix sizes. We find that serial execution outperforms parallel execution, especially for smaller matrices, but as matrix size increases, the performance gap widens. This suggests that parallelization's overhead can outweigh its advantages for larger matrices. Additionally, standard deviation in execution times increases with matrix size. Our case study uses the Ray framework on a 10-computer cluster provided by the University of Messina. The cluster performs our tests of determinant, dot product, matrix inversion, and rank calculations across different matrix sizes.
